Article Title

### 2014-01-27 plos.tex
minor

\section*{Acknowledgments}
We thank Genevera Allen for a helpful discussion, and Eftychios Pnevmatikakis for helpful suggestions and feedback on the manuscript.  This work was supported by grants NEI R01-EY018847, NEI P30-EY002520-33, NEI T32-EY07001-37, NIDA R01DA028525, the NIH-Pioneer award DP1-OD008301 to AST, the McKnight Scholar Award to AST; the Arnold & Beckman Foundation Young Investigator Award to AST; and NSF grants DMS-0817649, DMS-1122094 to KJ.
% The bibtex filename
\bibliography{references.bib}

>>>>

\section*{Acknowledgments}
We thank Genevera Allen for a helpful discussion, and Eftychios Pnevmatikakis for helpful suggestions and feedback on the manuscript.  This work was supported by grants NEI R01-EY018847, NEI P30-EY002520-33, NEI T32-EY07001-37, NIDA R01DA028525, the NIH-Pioneer award DP1-OD008301 to AST, the McKnight Scholar Award to AST; the Arnold \& Beckman Foundation Young Investigator Award to AST; and NSF grants DMS-0817649, DMS-1122094 to KJ.
% The bibtex filename
\bibliography{references.bib}
